Blocking-resistant communication\\through domain fronting

### 2014-07-26 docs/meek.tex
TLS camouflage revisions.

HTTP is fundamentally a request-based protocol.
There is no way for the server to ``push'' data to the client without
having first received a request.
In order to enable the server to send back data,
meek uses one of two techniques.
The first is polling:
every so often the client sends a request with an empty payload
if it has nothing else to send.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.
% Implemented in Psiphon's version.
The other technique is to use
long-lived persistent HTTP connections.
When the server sends a response, it keeps the connection open,
continually appending data to the response body while it has anything to send.
When the server receives a new request from the same client,
it closes any response it has open to the client and starts a new response.
See Section~\ref{sec:otherdeployment} for more details
on when each technique may be used.

\section{Making the TLS handshake indistinguishable}
\label{sec:browserextension}

The practice of routing traffic through a web service with domain fronting
defeats both address-based blocking and active scanning.
The endpoint (which appears to be the front domain; e.g. www.google.com)
cannot be blocked because to block it would cause collateral damage.
Active scanning is defeated because if the censor accesses the same
domain as does the client, all they see is a web page served by the front domain.
Even though the censor knows some traffic is being fronted,
by looking only at IP addresses and domain names, it cannot determine which.

However, a savvy censor may also use content-based blocking
(deep packet inspection) as a basis for blocking.
Anything that reliably distinguishes meek's traffic from that of normal allowed traffic
(presumably web browsing) must be eliminated.
In this section we demonstrate how the client part of the TLS handshake can be used
to fingerprint different TLS implementations,
and how we use a web browser to camouflage meek's TLS.

There are many parts of the TLS handshake, but the two that
most distinguish the client are the list of ciphersuites and the
list of TLS extensions in the ClientHello.
Figure~\ref{fig:ciphersuites} shows how the list of ciphersuites
differs in different client implementations.
Figure~\ref{fig:ciphersuites:meek-client} is how our first prototype of \meekclient\ appeared on the wire,
using the built-in crypto/tls library of the Go programming language.
The list of ciphersuites is unlike that of a web browser,
and could be used as a fingerprint for blocking.
Tor itself was blocked by China in 2011 in exactly this way~\cite{bug4744}.
Similarly the list of TLS extensions (not shown)
differed between \meekclient\ and popular browsers.

\begin{figure*}
\centering
\begin{subfigure}[t]{0.30\textwidth}
\begin{minipage}[t][17ex][t]{0.30\textwidth}
\tiny
\begin{verbatim}
TLS_ECDHE_RSA_WITH_AES_128_GCM_SHA256
TLS_ECDHE_ECDSA_WITH_AES_128_GCM_SHA256
TLS_ECDHE_RSA_WITH_RC4_128_SHA
TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
TLS_RSA_WITH_RC4_128_SHA
TLS_RSA_WITH_AES_128_CBC_SHA
TLS_RSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_RSA_WITH_3DES_EDE_CBC_SHA
TLS_RSA_WITH_3DES_EDE_CBC_SHA
\end{verbatim}
\end{minipage}
\caption{meek-client}
\label{fig:ciphersuites:meek-client}
\end{subfigure}
%
\begin{subfigure}[t]{0.30\textwidth}
\begin{minipage}[t][48ex][t]{0.30\textwidth}
\tiny
\begin{verbatim}
TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_ECDSA_WITH_3DES_EDE_CBC_SHA
TLS_ECDHE_RSA_WITH_3DES_EDE_CBC_SHA
TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
TLS_ECDHE_RSA_WITH_RC4_128_SHA
TLS_DHE_RSA_WITH_AES_128_CBC_SHA
TLS_DHE_DSS_WITH_AES_128_CBC_SHA
TLS_DHE_RSA_WITH_CAMELLIA_128_CBC_SHA
TLS_DHE_DSS_WITH_CAMELLIA_128_CBC_SHA
TLS_DHE_RSA_WITH_AES_256_CBC_SHA
TLS_DHE_DSS_WITH_AES_256_CBC_SHA
TLS_DHE_RSA_WITH_CAMELLIA_256_CBC_SHA
TLS_DHE_DSS_WITH_CAMELLIA_256_CBC_SHA
TLS_DHE_RSA_WITH_3DES_EDE_CBC_SHA
TLS_DHE_DSS_WITH_3DES_EDE_CBC_SHA
TLS_ECDH_ECDSA_WITH_AES_128_CBC_SHA
TLS_ECDH_RSA_WITH_AES_128_CBC_SHA
TLS_ECDH_ECDSA_WITH_AES_256_CBC_SHA
TLS_ECDH_RSA_WITH_AES_256_CBC_SHA
TLS_ECDH_ECDSA_WITH_3DES_EDE_CBC_SHA
TLS_ECDH_RSA_WITH_3DES_EDE_CBC_SHA
TLS_ECDH_ECDSA_WITH_RC4_128_SHA
TLS_ECDH_RSA_WITH_RC4_128_SHA
TLS_RSA_WITH_AES_128_CBC_SHA
TLS_RSA_WITH_CAMELLIA_128_CBC_SHA
TLS_RSA_WITH_AES_256_CBC_SHA
TLS_RSA_WITH_CAMELLIA_256_CBC_SHA
TLS_RSA_WITH_SEED_CBC_SHA
SSL_RSA_FIPS_WITH_3DES_EDE_CBC_SHA
TLS_RSA_WITH_3DES_EDE_CBC_SHA
TLS_RSA_WITH_RC4_128_SHA
TLS_RSA_WITH_RC4_128_MD5
\end{verbatim}
\end{minipage}
\caption{Firefox 24}
\label{fig:ciphersuites:firefox}
\end{subfigure}
%
\begin{subfigure}[t]{0.30\textwidth}
\begin{minipage}[t][27ex][t]{0.30\textwidth}
\tiny
\begin{verbatim}
TLS_ECDHE_ECDSA_WITH_AES_128_GCM_SHA256
TLS_ECDHE_RSA_WITH_AES_128_GCM_SHA256
TLS_DHE_RSA_WITH_AES_128_GCM_SHA256
TLS_ECDHE_ECDSA_WITH_CHACHA20_POLY1305_SHA256
TLS_ECDHE_RSA_WITH_CHACHA20_POLY1305_SHA256
TLS_RSA_WITH_AES_128_GCM_SHA256
TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
TLS_DHE_RSA_WITH_AES_256_CBC_SHA
TLS_RSA_WITH_AES_256_CBC_SHA
TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
TLS_ECDHE_RSA_WITH_RC4_128_SHA
TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
TLS_DHE_RSA_WITH_AES_128_CBC_SHA
TLS_DHE_DSS_WITH_AES_128_CBC_SHA
TLS_RSA_WITH_RC4_128_SHA
TLS_RSA_WITH_RC4_128_MD5
TLS_RSA_WITH_AES_128_CBC_SHA
TLS_RSA_WITH_3DES_EDE_CBC_SHA
\end{verbatim}
\end{minipage}
\caption{Chrome 33}
\label{fig:ciphersuites:chrome}
\end{subfigure}

\caption{Differences in ciphersuites offered by
our \meekclient\ program when it accesses the network directly,
and by two web browsers.
The distinctive ciphersuites offered by \meekclient\ can be used as part of a blocking fingerprint.
As a remedy we have \meekclient\ proxy its TLS through a web browser extension.
}
\label{fig:ciphersuites}
\end{figure*}

In response to the threat of TLS fingerprinting,
we modified \meekclient\ to proxy its HTTP requests through a local web browser extension.
\meekclient\ tells the extension what URLs to fetch, and the extension fetches them.
The TLS fingerprint looks like that of a browser, because it is that of a browser.
We implemented two versions of the extension, one for Firefox and one for Chrome.
They work similarly: they open a TCP port on localhost,
await instructions from \meekclient\ on what HTTP requests to make,
issue the requests, and return the responses.

\begin{figure}
\centering
\includegraphics[height=1.5in]{browser-architecture}
\caption{
Client architecture including a browser extension for TLS camouflage.
Dashed lines show the process hierarchy.
Solid lines show the flow of outgoing communication.
The headless instance of the browser runs in the background and is invisible to the user.
This figure is a zoomed-in view of the ``Client's PC'' component of Figure~\ref{fig:architecture}.
}
\label{fig:browser-architecture}
\end{figure}

Figure~\ref{fig:browser-architecture} shows the interaction of components
on the user's computer.
Rather than starting \meekclient\ as a pluggable transport directly, the Tor
process starts a helper process that starts both \meekclient\
and a headless browser instance.
The headless browser runs our extension in a separate
process and separate browser profile from the browser the
user interacts with; the two browser instances share no state.
\meekclient\ is configured to issue its requests through the browser extension;
in this configuration, the headless browser is the only thing that ever touches the network.
When run with a browser extension, meek has the same TLS signature
as Firefox (Figure~\ref{fig:ciphersuites:firefox}) or
Chrome (Figure~\ref{fig:ciphersuites:chrome}).

The use of a browser extension offers benefits beyond its TLS signature.
We inherit other characteristics of the browser:
how often it resolves DNS names,
its connection reuse,
and HTTP keepalive behavior.
The Firefox extension has special usability advantages because the Tor Browser Bundle
uses a modified Firefox.
We can include a small extension in the browser bundle, reusing the existing
Firefox executable, without increasing the download size of the bundle much,
and without requiring users to separately configure a browser to run the extension.

The development of the browser extensions posed some unexpected challenges.
Tor Browser disables TLS session tickets because they can be used as linking identifiers,
but the lack of session tickets shows up as a missing TLS extension,
so we had to reenable them in the headless browser.
(Doing so doesn't harm Tor Browser's anonymity:
if session tickets are used, they are used only on the circumvention layer
between the user and the frontend server. Tor Browser's own TLS is tunneled
within the circumvention layer, and session tickets are still disabled at that level.)
The Chrome extension needed to be split into two pieces, an extension and an app,
because an extension cannot open a listening socket and an app cannot make HTTP requests.

@@

>>>>

HTTP is fundamentally a request-based protocol.
There is no way for the server to ``push'' data to the client without
having first received a request.
In order to enable the server to send back data,
meek uses one of two techniques.
The first is polling:
every so often the client sends a request with an empty payload
if it has nothing else to send.
The polling interval starts short (100~ms) and grows exponentially
up to a maximum of 5~s.
% Implemented in Psiphon's version.
The other technique is to use
long-lived persistent HTTP connections.
When the server sends a response, it keeps the connection open,
continually appending data to the response body while it has anything to send.
When the server receives a new request from the same client,
it closes any response it has open to the client and starts a new response.
See Section~\ref{sec:otherdeployment} for more details
on when each technique may be used;
it depends on the intermediate web service.

\section{Camouflage for the TLS layer}
\label{sec:browserextension}

Domain fronting defeats address-based blocking and active probing.
HTTPS foils the most straightforward DPI,
hiding byte patterns in the underlying stream.
The censor may try to apply more careful DPI in order to
distinguish fronted and non-fronted traffic.
This section is about TLS fingerprinting,
which is the censor's remaining easy distinguisher,
and how we use a web browser with an unremarkable TLS fingerprint
to disguise the HTTPS tunnel.
The next section is about more subtle and hard-to-apply forms of DPI.

The TLS handshake is largely plaintext~\cite[Section~7.4]{rfc5246}.
The plaintext SNI extension, for instance, has to be protected by domain fronting.
There is enough room for variation in other fields,
such as the client's lists of ciphersuites and extensions,
that it is possible to fingerprint different client TLS implementations~\cite{ssl-p0f}.
(We are only concerned with fingerprinting the client,
because the server's TLS that the censor can observe
comes from the intermediate web service;
i.e., it is what you would expect when connecting to the front domain.)
Tor itself was blocked by China in 2011
because of the distinctive ciphersuite list it used at that time~\cite{bug4744}.

Figure~\ref{fig:ciphersuites} shows examples of how TLS client
implementations may differ.
Figure~\ref{fig:ciphersuites:golang} is from the Go programming languages
built-in net/http library~\cite{golang-net/http},
which has a custom TLS implementation;
it is how \meekclient\ would appear with no TLS camouflage.
It is unlike Figures~\ref{fig:ciphersuites:firefox} and~\ref{fig:ciphersuites:chrome},
which are browsers; the browsers are also unlike each other.
A censor could block an uncamouflaged meek using Go's fingerprint,
if it considered the collateral damage resulting from blocking other Go programs to be slight enough.

\begin{figure*}
\centering
\begin{subfigure}[t]{0.30\textwidth}
\caption{Go 1.2's net/http library}
\begin{minipage}[t][25.5ex][t]{\textwidth}
\tiny
\begin{verbatim}
Ciphersuites:
  TLS_ECDHE_RSA_WITH_AES_128_GCM_SHA256
  TLS_ECDHE_ECDSA_WITH_AES_128_GCM_SHA256
  TLS_ECDHE_RSA_WITH_RC4_128_SHA
  TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
  TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
  TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
  TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
  TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
  TLS_RSA_WITH_RC4_128_SHA
  TLS_RSA_WITH_AES_128_CBC_SHA
  TLS_RSA_WITH_AES_256_CBC_SHA
  TLS_ECDHE_RSA_WITH_3DES_EDE_CBC_SHA
  TLS_RSA_WITH_3DES_EDE_CBC_SHA
Extensions:
  server_name
  status_request
  elliptic_curves
  ec_point_formats
  signature_algorithms
\end{verbatim}
\end{minipage}
\label{fig:ciphersuites:golang}
\end{subfigure}
%
\begin{subfigure}[t]{0.30\textwidth}
\caption{Firefox 24}
\begin{minipage}[t][57ex][t]{\textwidth}
\tiny
\begin{verbatim}
Ciphersuites:
  TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
  TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
  TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
  TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
  TLS_ECDHE_ECDSA_WITH_3DES_EDE_CBC_SHA
  TLS_ECDHE_RSA_WITH_3DES_EDE_CBC_SHA
  TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
  TLS_ECDHE_RSA_WITH_RC4_128_SHA
  TLS_DHE_RSA_WITH_AES_128_CBC_SHA
  TLS_DHE_DSS_WITH_AES_128_CBC_SHA
  TLS_DHE_RSA_WITH_CAMELLIA_128_CBC_SHA
  TLS_DHE_DSS_WITH_CAMELLIA_128_CBC_SHA
  TLS_DHE_RSA_WITH_AES_256_CBC_SHA
  TLS_DHE_DSS_WITH_AES_256_CBC_SHA
  TLS_DHE_RSA_WITH_CAMELLIA_256_CBC_SHA
  TLS_DHE_DSS_WITH_CAMELLIA_256_CBC_SHA
  TLS_DHE_RSA_WITH_3DES_EDE_CBC_SHA
  TLS_DHE_DSS_WITH_3DES_EDE_CBC_SHA
  TLS_ECDH_ECDSA_WITH_AES_128_CBC_SHA
  TLS_ECDH_RSA_WITH_AES_128_CBC_SHA
  TLS_ECDH_ECDSA_WITH_AES_256_CBC_SHA
  TLS_ECDH_RSA_WITH_AES_256_CBC_SHA
  TLS_ECDH_ECDSA_WITH_3DES_EDE_CBC_SHA
  TLS_ECDH_RSA_WITH_3DES_EDE_CBC_SHA
  TLS_ECDH_ECDSA_WITH_RC4_128_SHA
  TLS_ECDH_RSA_WITH_RC4_128_SHA
  TLS_RSA_WITH_AES_128_CBC_SHA
  TLS_RSA_WITH_CAMELLIA_128_CBC_SHA
  TLS_RSA_WITH_AES_256_CBC_SHA
  TLS_RSA_WITH_CAMELLIA_256_CBC_SHA
  TLS_RSA_WITH_SEED_CBC_SHA
  SSL_RSA_FIPS_WITH_3DES_EDE_CBC_SHA
  TLS_RSA_WITH_3DES_EDE_CBC_SHA
  TLS_RSA_WITH_RC4_128_SHA
  TLS_RSA_WITH_RC4_128_MD5
Extensions:
  server_name
  renegotiation_info
  elliptic_curves
  ec_point_formats
  SessionTicket TLS
  next_protocol_negotiation
\end{verbatim}
\end{minipage}
\label{fig:ciphersuites:firefox}
\end{subfigure}
%
\begin{subfigure}[t]{0.30\textwidth}
\caption{Chrome 33}
\begin{minipage}[t][42.5ex][t]{\textwidth}
\tiny
\begin{verbatim}
Ciphersuites:
  TLS_ECDHE_ECDSA_WITH_AES_128_GCM_SHA256
  TLS_ECDHE_RSA_WITH_AES_128_GCM_SHA256
  TLS_DHE_RSA_WITH_AES_128_GCM_SHA256
  TLS_ECDHE_ECDSA_WITH_CHACHA20_POLY1305_SHA256
  TLS_ECDHE_RSA_WITH_CHACHA20_POLY1305_SHA256
  TLS_RSA_WITH_AES_128_GCM_SHA256
  TLS_ECDHE_ECDSA_WITH_AES_256_CBC_SHA
  TLS_ECDHE_RSA_WITH_AES_256_CBC_SHA
  TLS_DHE_RSA_WITH_AES_256_CBC_SHA
  TLS_RSA_WITH_AES_256_CBC_SHA
  TLS_ECDHE_ECDSA_WITH_RC4_128_SHA
  TLS_ECDHE_ECDSA_WITH_AES_128_CBC_SHA
  TLS_ECDHE_RSA_WITH_RC4_128_SHA
  TLS_ECDHE_RSA_WITH_AES_128_CBC_SHA
  TLS_DHE_RSA_WITH_AES_128_CBC_SHA
  TLS_DHE_DSS_WITH_AES_128_CBC_SHA
  TLS_RSA_WITH_RC4_128_SHA
  TLS_RSA_WITH_RC4_128_MD5
  TLS_RSA_WITH_AES_128_CBC_SHA
  TLS_RSA_WITH_3DES_EDE_CBC_SHA
Extensions:
  server_name
  renegotiation_info
  elliptic_curves
  ec_point_formats
  SessionTicket TLS
  next_protocol_negotiation
  application_layer_protocol_negotiation
  Channel ID
  status_request
  signature_algorithms
  Signed Certificate Timestamp
\end{verbatim}
\end{minipage}
\label{fig:ciphersuites:chrome}
\end{subfigure}

\caption{
Selected differences in ClientHello messages in three different TLS implementations.
}
\label{fig:ciphersuites}
\end{figure*}

In order to disguise its TLS fingerprint,
\meekclient\ proxies all its HTTPS requests through an actual web browser.
We implemented extensions for two web browsers,
Firefox and Chrome,
that enable them to make HTTPS requests on behalf of \meekclient.
The TLS fingerprint looks like that of a browser, because it is that of a browser.
The browser instance with the extension is completely separate
from the browser the user interacts with.
It runs invisibly in the background in a separate process,
doesn't display a user interface,
and shares no state with the user's browser.

\begin{figure}
\centering
\includegraphics[height=1.5in]{browser-architecture}
\caption{
Client architecture including a browser extension for TLS camouflage.
Dashed lines show the process hierarchy.
Solid lines show the flow of outgoing communication.
The headless browser runs in the background and is invisible to the user.
This figure is a zoomed-in view of the ``Client's PC'' component of Figure~\ref{fig:architecture}.
}
\label{fig:browser-architecture}
\end{figure}

Figure~\ref{fig:browser-architecture} shows the interaction of components
on the client's computer.
The local Tor process starts a helper process that starts both \meekclient\
and the headless browser,
then configures \meekclient\ to proxy its requests through the browser extension.
The user's browser proxies through Tor;
Tor proxies through \meekclient,
and \meekclient\ proxies through the headless browser.
The headless browser is the only thing that ever actually touches the network.
It should be emphasized that the URLs requested by the headless browser extension
have no relation to the URLs the user actually browses;
the extension only ever makes requests to the front domain.

The use of a browser extension brings benefits beyond TLS camouflage.
It means meek inherits other traffic characteristics of the browser:
for instance
how often it resolves DNS names,
its connection reuse,
and its HTTP keepalive behavior.
The Firefox extension has special advantages
when meek is used with Tor Browser
because Tor Browser
is a modified version of Firefox.
We can use the same browser executable for both the browser the user interacts with (Tor Browser)
and the one providing TLS camouflage (a headless Firefox),
saving space in distribution packages
and sparing the user from having to separately configure a browser to run the extension.
In Tor Browser,
the headless Firefox is started and stopped transparently
when meek is activated and deactivated.

% The development of the browser extensions posed some unexpected challenges.
% Tor Browser disables TLS session tickets because they can be used as linking identifiers,
% but the lack of session tickets shows up as a missing TLS extension,
% so we had to reenable them in the headless browser.
% (Doing so doesn't harm Tor Browser's anonymity:
% if session tickets are used, they are used only on the circumvention layer
% between the user and the frontend server. Tor Browser's own TLS is tunneled
% within the circumvention layer, and session tickets are still disabled at that level.)
% The Chrome extension needed to be split into two pieces, an extension and an app,
% because an extension cannot open a listening socket and an app cannot make HTTP requests.

No TLS camouflage is needed between the intermediate web service and \meekserver,
because that portion of the communication flow is not observed by the censor.

Appropriate TLS camouflage may differ according to circumstances.
On a traditional desktop PC, using a browser is probably the right choice.
When Psiphon ported \meekclient\ to Android,
they didn't use a browser as camouflage,
but rather made all HTTPS requests with the standard Android HTTP API.
This decision makes sense because typical Android applications
also use the standard API and share the same TLS fingerprint.

@@

% Advantage is that we are probably proxying web traffic.
